---
title: "How to use animatoR with Rmarkdown "
author: "Andrej Blejec"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HowTo-use-animatoR-with-Rmarkdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r initialize,echo=FALSE,results='hide'}
options(width=70)
library(animatoR)
```

This is a short example to show how to embed `animatoR` based animations
into Rmarkdown generated HTML file.

For embedding one can use the figure chunk option
`fig.show='animate'`.
Option `interval` controls the smoothness of
the replay.
Size is set by the option `out.width`.

Here are the chunk options used for this example

> {fig.show='animate',interval=0.01,results="asis"}


```{r fig.show='animate',interval=0.01,results="asis",eval=FALSE}
animator(
"newplot();box();tpoints(2,2,8,8,cex=2,pch=16)"
,life=2)
```
(Note: chunk is not evaluated, can not set Travis-ci to use ffmpeg properly).

To view and run the animation, you have to open the HTML file in a browser.


## SessionInfo

```{r sessionInfo,echo=FALSE}
cat(win.version())
sessionInfo()
cat("Project path:`",dirname(getwd()),"`\\\\\n")
```
