---
title: "HowTo Use **animatoR** in **Rmarkdown**"
author: "A. Blejec"
date: "13 August 2016"
output:
  html_document: default
  pdf_document: default
---

```{r include=FALSE}
library(knitr)
opts_chunk$set(
fig.path='./figs/kn',concordance=TRUE
)
```



```{r initialize,echo=FALSE,results='hide'}
options(width=70)
library(animatoR)
library(knitr)
```

This is a short example to show how to embed `animatoR` based animations
into Rmarkdown generated HTML file.

For embedding we can use the figure chunk option
`fig.show='animate'`.
Option `interval` controls the smoothness of
the replay.
Size is set by the option `out.width`.

Here are the chunk options used for this example

> {fig.show='animate',interval=0.01,results="asis"}


```{r fig.show='animate',interval=0.01,results="asis"}
animator(
"newplot();box();tpoints(2,2,8,8,cex=2,pch=16)"
,life=2)
```

To view and run the animation, you have to open the HTML file in a browser.


## SessionInfo

```{r sessionInfo,echo=FALSE}
cat(win.version())
sessionInfo()
cat("Project path:`",dirname(getwd()),"`\\\\\n")
```


